Paper Results Section

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd
added filter to plot, updated some counts

r_b_f <- read_rds("../data/final_obs_counts_df.RDS")
as.tibble(r_b_f) %>%
  mutate(names = row.names(records_by_fun)) %>%
  rename(obs = invo_obs) %>%
  select(names, obs) -> records_by_fun

total_recorded_sigs %>%
  inner_join(records_by_fun, by="names") %>%
  filter(obs != 0, rec !=0) %>% 
  inner_join(cloc, by="names") %>%
  filter(r_counts != 0) -> df

>>>>

r_b_f <- read_rds("../data/final_obs_counts_df.RDS")
as.tibble(r_b_f) %>%
  mutate(names = row.names(r_b_f)) %>%
  rename(obs = invo_obs) %>%
  select(names, obs) -> records_by_fun

total_recorded_sigs %>%
  inner_join(records_by_fun, by="names") %>%
  filter(obs != 0, rec !=0) %>% 
  inner_join(cloc, by="names") %>%
  filter(rec <= obs) %>%                      # Added this
  filter(r_counts != 0) -> df

### 2019-03-26 notebooks/paper_results_section.Rmd
data and playing with plots
notebooks
added filter to plot, updated some counts

Get the counts.
```{r}
# argument counts
total_arguments <- apply_count_to_lopkg_c(los, args_count_all)
total_mono_type <- apply_count_to_lopkg_c(los, args_count_all_mono_type)
total_mono_attr <- apply_count_to_lopkg_c(los, args_count_all_mono_attr_pattern)
total_mono_clas <- apply_count_to_lopkg_c(los, args_count_all_mono_class)
total_mono_all <- apply_count_to_lopkg_c(los, args_count_all_mono_all)
```

```{r}
tot_arg_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=round(c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments) / 1000, 0),
  Percentage=round(c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments) / total_arguments * 100, 2)
)

xtable(tot_arg_df)
```

```{r}
# function counts
total_functions <- apply_count_to_lopkg_c(los, length)
total_mono_type_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_type)
total_mono_attr_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_attr_pattern)
total_mono_clas_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_class)
total_mono_all_functions <- apply_count_to_lopkg_c(los, fun_count_all_mono_all)
```

```{r}
tot_fun_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=round(c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions) / 1000, 0),
  Percentage=round(c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions) / total_functions * 100, 2)
)

xtable(tot_fun_df)
```

@@

>>>>

Get the counts.
```{r}
# argument counts
c_basic_df <- build_arg_count_df_from_lopkgs(los)

xtable(c_basic_df)
```

```{r}
# function counts
c_f_basic_df <- build_fun_count_df_from_lopkgs(los)

xtable(c_f_basic_df)
```

@@

Generate...
```{r}
xtable(null_na_fold_real_arg_counts)
xtable(null_na_fold_real_fun_counts)
```

Top sig time.
```{r}
poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```
